data wrangling and plots

### 2021-02-22 shared analysis files /data_wrangling_plot22feb.Rmd
updated plots

```{r}
##wrangling calculations for metafor

@@

```{r}
# data wrangling for plots
count(dat_MA_ES, flux_range) #46 rows w/ range of 10, 51 w/ range of 15, 36 w/range of 6
count(dat_MA_ES, resp_units)
count(dat_MA_ES, mean_temp_constant, study_id) #24 C common accross 5 studies
count(dat_MA_ES, resp_def, sort = TRUE)
count(dat_MA_ES, genus)
count(dat_MA_ES, genus, study_id)
count(dat_MA_ES, resp_units) # body mass, avg. cum. num of eggs laid/fm, avg. num of eggs laid/fm, survival, rate of change, are the the most common reponses

normalized <- dat_MA_ES %>%
  filter(yi > -20)

common_unit_C <-dat_MA_ES %>% 
  filter(resp_units == "C")

common_unit_g <-dat_MA_ES %>% 
filter(resp_units == "g")
#filtering for genus to only be drosophila 
drosophila <- dat_MA_ES %>% 
  filter(genus == "Drosophila")

#filtering for just flux ranges of 10 C 
common_range <- dat_MA_ES %>% 
  filter(flux_range == "10")
#filtering for just studies with mean temp of 24
common_temp <- dat_MA_ES %>% 
  filter(mean_temp_constant == "24")

count(dat_MA_ES, larger_group)
count(dat_MA_ES, genus)
count(dat_MA_ES, genus, study_id)

#Drosophila used across 4 studies, potential to aggregate based on that?

#16 genuses to aggregate across 
count(dat_MA_ES, mean_temp_constant)

```

```{r}
#SMD across all studies
ggplot(normalized, aes(x=study_id, y=yi))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 10, angle = 45))+
  ggtitle("SMD across all studies")
```

```{r}
# scatterplot of standardized mean response faceted by exp age
ggplot(dat_MA_ES, aes(x=log(vi), y=log(yi), color = study_id))+
  geom_point()+
  theme_bw()+
  facet_wrap(~exp_age)+
  ggtitle("Log transformed SMD across log transformed variance 
          colored by study and faceted by experimental age")
```

```{r}
# scatterplot of standardized mean response vs mean temp faceted by org level and colored by flux_range
ggplot(dat_MA_ES, aes(x=mean_temp_constant, y=yi, color = as.factor(flux_range)))+
  geom_point()+
  facet_wrap(~org_level)+
  theme_bw()+
  ggtitle("SMD across mean temperature colored by fluctation range 
          and faceted by organization level")
```

```{r}
# scatterplot of standardized mean response vs flux range colored and lm fit by org level
ggplot(boxplot, aes(x=flux_range, y=yi, color = as.factor(org_level)))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  ggtitle("SMD across fluctuation ranges colored by organization level 
          and fit with linear model")
```

```{r}
ggplot(boxplot, aes(x=flux_range, y=yi, color = study_id))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  theme_minimal()+
  ggtitle("SMD across fluctuation ranges colored by 
          studies and fit with linear model by study")
```

```{r}
#trying to look at drosophila response across studies 
ggplot(drosophila, aes(y=yi, x=study_id, color = study_id))+
  geom_boxplot()+
  theme_minimal()+
  ggtitle("SMD across studies with the same study genus (Drosophila)")
```

```{r}
ggplot(normalized, aes(y=yi, x=flux_range, color = genus))+
  geom_jitter()+
  theme_minimal()+
  ggtitle("SMD across fluctuation ranges colored by genus")
```

```{r}
ggplot(normalized, aes(y=yi, x=flux_range, color = genus))+
  geom_jitter()+
  theme_minimal()+
  facet_wrap(~size)+
  ggtitle("SMD across fluctuation ranges colored by genus")
```

```{r}
#looking at yi across studies with the same temperature range (10 C)
ggplot(common_range, aes(y=yi, x=study_id, color = study_id))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
                                  ggtitle("SMD across studies with the same 
                                          temperature fluctuation range (10 C)")
```

```{r}
#looking at yi across studies with the same mean temperature (24 C)
ggplot(common_temp, aes(y=yi, x=study_id, color = study_id))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("SMD across studies with the same mean temperature (24 C)")
```

```{r}
#trying to look at how size trends yi across increasing flux ranges 
ggplot(normalized, aes(y=abs(yi), x=flux_range, color = as.factor(size)))+
  geom_point(alpha = 0.5)+
  geom_smooth(formula = y~x)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("Absolute SMD across fluctuation ranges colored 
          by size of study organism and fitted with model curve")
```

```{r}
ggplot(common_unit_C, aes(y=yi, x=study_id, color = as.factor(flux_range)))+
  geom_point(alpha = 0.5)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("SMD across studies with the common unit C (CT assays)")
```

```{r}
#plot across studies with common unit gram
ggplot(common_unit_g, aes(y=yi, x=flux_range, color = study_id))+
  geom_point(alpha =0.5)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
  ggtitle(SMD across fluctuation ranges colored by studies with the common unit "grams")
```

>>>>

```{r, echo= FALSE}
##wrangling calculations for metafor

@@

```{r, echo= FALSE}
## data wrangling for plots
#count and propotions for the different variables
count(dat_MA_ES, flux_range) #46 rows w/ range of 10, 51 w/ range of 15, 36 w/range of 6
count(dat_MA_ES, resp_units, sort = TRUE) 
count(dat_MA_ES, mean_temp_constant, study_id) #24 C common accross 5 studies
count(dat_MA_ES, resp_def, sort = TRUE) # body mass, avg. cum. num of eggs laid/fm, avg. num of eggs laid/fm, survival, rate of change, are the the most common reponses
count(dat_MA_ES, genus, study_id) # 3 studies featuring drosophila
count(dat_MA_ES, genus)# 16 genuses to bin by 
count(dat_MA_ES, size)# good spread for body size
count(dat_MA_ES, larger_group) # pretty much mostly animal studies

#removing outlier point to get better picture of data structure
normalized <- dat_MA_ES %>%
  filter(yi > -20) 
#filtering for studies with common variable C (CT assays)
common_unit_C <-dat_MA_ES %>% 
  filter(resp_units == "C")
#filtering for studies with common variable g 
common_unit_g <-dat_MA_ES %>% 
filter(resp_units == "g")
#filtering for genus to only be drosophila 
drosophila <- dat_MA_ES %>% 
  filter(genus == "Drosophila")
#filtering for just flux ranges of 10 C 
common_range <- dat_MA_ES %>% 
  filter(flux_range == "10")
#filtering for just studies with mean temp of 24
common_temp <- dat_MA_ES %>% 
  filter(mean_temp_constant == "24")
```

```{r, echo= FALSE}
#SMD across all studies
ggplot(normalized, aes(x=study_id, y=yi))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 10, angle = 45))+
  ggtitle("SMD across all studies")
```

```{r, echo= FALSE}
# scatterplot of standardized mean response faceted by exp age
ggplot(dat_MA_ES, aes(x=log(vi), y=log(yi), color = study_id))+
  geom_point()+
  theme_bw()+
  facet_wrap(~exp_age)+
  ggtitle("Log transformed SMD across log transformed variance 
          colored by study and faceted by experimental age")
```

```{r, echo= FALSE}
# scatterplot of standardized mean response vs mean temp faceted by org level and colored by flux_range
ggplot(dat_MA_ES, aes(x=mean_temp_constant, y=yi, color = as.factor(flux_range)))+
  geom_point()+
  facet_wrap(~org_level)+
  theme_bw()+
  ggtitle("SMD across mean temperature colored by fluctation range 
          and faceted by organization level")
```

```{r, echo= FALSE}
# scatterplot of standardized mean response vs flux range colored and lm fit by org level
ggplot(normalized, aes(x=flux_range, y=yi, color = as.factor(org_level)))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  ggtitle("SMD across fluctuation ranges colored by organization level 
          and fit with linear model")
```

```{r, echo= FALSE}
ggplot(normalized, aes(x=flux_range, y=yi, color = study_id))+
  geom_point()+
  geom_smooth(method="lm", formula = y~x)+
  theme_minimal()+
  ggtitle("SMD across fluctuation ranges colored by 
          studies and fit with linear model by study")
```

```{r, echo= FALSE}
#trying to look at drosophila response across studies 
ggplot(drosophila, aes(y=yi, x=study_id, color = study_id))+
  geom_boxplot()+
  theme_minimal()+
  ggtitle("SMD across studies with the same study genus (Drosophila)")
```

```{r, echo= FALSE}
ggplot(normalized, aes(y=yi, x=flux_range, color = genus))+
  geom_jitter(alpha = 0.5)+
  theme_minimal()+
  ggtitle("SMD across fluctuation ranges colored by genus")
```

```{r, echo= FALSE}
#looking at yi across studies with the same temperature range (10 C)
ggplot(common_range, aes(y=yi, x=study_id, color = study_id))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
                                  ggtitle("SMD across studies with the same 
                                          temperature fluctuation range (10 C)")
```

```{r, echo= FALSE}
#looking at yi across studies with the same mean temperature (24 C)
ggplot(common_temp, aes(y=yi, x=study_id, color = study_id))+
  geom_boxplot()+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("SMD across studies with the same mean temperature (24 C)")
```

```{r, echo= FALSE}
#trying to look at how size trends yi across increasing flux ranges 
ggplot(normalized, aes(y=abs(yi), x=flux_range, color = as.factor(size)))+
  geom_point(alpha = 0.5)+
  geom_smooth(formula = y~x)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("Absolute SMD across fluctuation ranges colored 
          by size of study organism and fitted with model curve")
```

```{r, echo= FALSE}
ggplot(common_unit_C, aes(y=yi, x=study_id, color = as.factor(flux_range)))+
  geom_point(alpha = 0.5)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                   size = 7, angle = 45))+
  ggtitle("SMD across studies with the common unit C (CT assays)")
```

```{r, echo= FALSE}
#plot across studies with common unit gram
ggplot(common_unit_g, aes(y=yi, x=flux_range, color = study_id))+
  geom_point(alpha =0.5)+
  theme_minimal()+
  theme(axis.text.x = element_text(face = "bold", 
                                  size = 7, angle = 45))+
  ggtitle("SMD across fluctuation ranges colored by studies with the common unit grams")
```
